The prime of their life - the halflife of acting talent

### 2017-09-04 01_halflife-of-acting-talent/article.Rmd
button

Unfortunately, because the Rotten Tomatoes development team are a bunch of politically correct SJWs, gender isn't provided on their film bio pages so we'll have to be creative. The `gender` R package allows you to infer a person's gender from their first name and DOB. The result is a probabilistic estimate of that individuals most likely gender given their first name and the year they were born.

@@

<button class="button secondary outline" id = "update_age_series"> Show Cumulative Distribution </button>

>>>>

Unfortunately, because the Rotten Tomatoes development team are a bunch of politically correct SJWs (/s), gender isn't provided on their film bio pages so we'll have to be creative. The `gender` R package allows you to infer a person's gender from their first name and DOB. The result is a probabilistic estimate of that individuals most likely gender given their first name and the year they were born.

@@

<button class="button w100 secondary round outline" id = "update_age_series"> Show Cumulative Distribution </button>
